\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{#3} & \text{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\urlNewWindow}[1]{\href[pdfnewwindow=true]{#1}}
%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Nikita Pardeshi}} & Email: \urlNewWindow{mailto:}{ngp15@georgetown.edu}\\
  \urlNewWindow{http://nikita-pardeshi.netlify.app}{Portfolio: http://nikita-pardeshi.netlify.app} & Mobile: +1 571-771-9725 \\
  \urlNewWindow{https://github.com/Nikita-Pardeshi}{Github: github.com/Nikita-Pardeshi} \\
  \urlNewWindow{https://www.linkedin.com/in/nikita-pardeshi25/}{LinkedIn: https://www.linkedin.com/in/nikita-pardeshi25/} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgetown University- The Graduate School of Arts and Sciences}{Washington, DC}
      {Master of Science in Data Science and Analytics;  GPA: 3.83/4.0}{August 2021 - May 2023}

      \vspace{1pt}
      {\small\text{Awarded Returning Student Scholarship based on \urlNewWindow{https://nikita-pardeshi-evaluate-cybersecurity-threat.netlify.app/}{project submission}}}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{\justifying Relevant Coursework:} Introduction to Data Science and Analytics, Statistics and Probability, Optimization, Big Data and Cloud Computing, Statistical Inference, Advanced Data Visualization, Natural Language Processing, Neural Networks}}}
    \resumeSubHeadingListEnd
	    
\vspace{-9pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages:}{~~~~~~Python, R, HTML, JavaScript, SQL, Bash}
	\resumeSubItem{Frameworks:}{~~~~Scikit, NLTK, SpaCy, TensorFlow, Keras, Django, Flask, Apache Spark, Spark SQL, Hadoop MapReduce, HiveQL, AutoML, Scipy, Multiprocessing, InterpretML}
	\resumeSubItem{Tools:}{~~~~~~~~~~~~~~Docker, GIT, PostgreSQL, MySQL, SQLite, Tableau, Power BI, Atlassian- Jira, Confluence}
	\resumeSubItem{Platforms:}{~~~~~~~Linux, Windows, AWS- EC2, Lambda, S3, Cloud9, Sagemaker, EMR, Hadoop User Experience (HUE)}

\resumeSubHeadingListEnd
\vspace{-6pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Ready Tensor Inc.}{San Diego, CA}
    {Machine Learning Engineer Intern}{June 2022 - August 2022}
    \resumeItemListStart
        \resumeItem{}
          {Developed ML algorithms- AdaBoost, XGBoost, Elasticnet, Random Forest, Stochastic Gradient Descent, SVM, ARIMA, SARIMA, Exponential Smoothing in Python and R. Apply Hyperparameter tuning.}
          \resumeItem{}
          {Provide users with Model interpretability and explainability features using InterpretML, LIME and SHapley in Python.}
          \resumeItem{}
          {Created docker images for training and testing the models in real time on different platforms and OS. Deployed models on AWS using SageMaker, Lambda and EC2.}
          \vspace{4pt}
      \resumeItemListEnd
\vspace{-5pt}
    \resumeSubheading
		{SkyQuest Technology Group}{Remote}
		{Data Science Executive}{January 2021 -  July 2021}
		\resumeItemListStart
        \resumeItem{}
          {Collaborated on R&D dashboard for Reckitt – data collection, creating APIs in Flask and Django, database design and management, custom BERT models for automated categorization with a focus on News Analytics (NLP) having an accuracy of 85\%. }
        \resumeItem{}
          {Hands on experience with Atlassian Jira and Confluence for Agile Project Management.}
        \resumeItem{}{Automated Company Earnings Call transcript’s collection, indexing and searching, summarization, text analytics and visualization. Lead a team of 10 data science interns.}
		\resumeItemListEnd
  \vspace{0.5pt}
  \resumeSubheading
            {SkyQuest Technology Group}{Remote}
		{Data Analyst Intern}{May 2020 -  December 2020}
		\resumeItemListStart
        \resumeItem{}
          {Developed web applications in Django and Python, Automated Data Collection bot using Selenium and Scrapy.}
        \resumeItem{}
          {Collected macro and micro economic indicators, Patent data Analysis, Network Analytics in Power BI.}
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-10pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{\urlNewWindow{https://gender-disparity-in-workplace.netlify.app/}{Gender Disparity in Workplace}}
{ (January 2022 - May 2022) Interactive, Data-driven Visual Narrative showcasing the different findings and corresponding reasons for gender disparity across
different fields. The project targets laws and regulations across countries and impact in the workforce along with analyzing
social media tweets and news. \\
Tech: Python- Plotly, NLTK, NewsAPI, Altair; JavaScript, HTML, CSS, R.}
\vspace{1pt}

\resumeSubItem{\urlNewWindow{https://ngpardeshi.georgetown.domains/big-data/index.html}{CryptoCurrency Subreddit Analysis- Big Data Project}}
{ (January 2022 - May 2022) Collected 7M+ subreddit comment and post data, analyzed and forecasted Cryptocurrency prices based on activity in Subreddit using Apache Spark and Spark SQL in Python and AWS cloud. 
Tech: Python, Apache Spark, Spark SQL, Hadoop User Experience (HUE), AWS, NLP, Plotly}
\vspace{1pt}

\resumeSubItem{\urlNewWindow{https://github.com/Nikita-Pardeshi/Financial-Analytics}{Financial Statement Analysis}}
{ (August 2020 - December 2020) Gathered company specific income statement, balance sheet and cash flows through Yahoo Finance API, performed horizontal (trend) and vertical (Y-O-Y) analysis of financial statements and generated a final report in Python. Tech: Python, APIs, Django, Plotly.}
\vspace{1pt}

% -- \resumeSubItem{LinkedIn Social Network Analysis}{ (September 2020 - October 2020) Network Analysis to reach out to top management and relevant employees on LinkedIn through 1st, 2nd and 3rd degree connections for marketing, deals and other business proposals. Tech: Python, Power BI, APIs.} \vspace{1pt}-- %

\resumeSubItem{\urlNewWindow{}{Johnson\&Johnson Quarterly Earnings Prediction in R (SARIMA model)}}{ (March 2020) Understand trend and seasonality and fitting SARIMA model to forecast J&J share price in R. Tech: R.}
\vspace{1pt}

\resumeSubHeadingListEnd
\vspace{-6pt}

%---- Publications --% 
\section{Publications}
\resumeSubHeadingListStart
\resumeSubItem{\urlNewWindow{https://www.irjet.net/archives/V7/i4/IRJET-V7I4837.pdf}{Machine Learning/ Deep Learning Based Recommendation System}}{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~IJRET (April 2020)}
\vspace{2pt}
\resumeSubItem{\urlNewWindow{https://irjet.net/archives/V7/i4/IRJET-V7I4838.pdf}{An Empirical Study of Support Vector Machine and Naïve \\ Bayes Classifier using Python And R}}{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~IJRET (April 2020)}
\resumeSubHeadingListEnd

%-----------Awards-----------------
% \section{Honors and Awards}
% \begin{description}[font=$\bullet$]
% \item {Awarded merit and project based Returning Student Scholarship % \text{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~June 2022}}
% \end{description}

%--- Extracurricular ---% 

\vspace{-2.5pt}
\section{Extracurricular}
  \resumeSubHeadingListStart

\resumeSubheading
    {Data Annotator}{Georgetown University}
    {Data Validation, indexing and searching and query databases using SQL and regex}{Jan 2022 - Present}
    
\vspace{1pt}
    \resumeSubheading
    {Student Ambassador}{Georgetown University}
    {Managed administrative work and organized events for Graduate Students.}{August 2021 - Present}
    
\vspace{1pt}
    \resumeSubheading
    {Teaching Assistant}{Georgetown University}
    {Blockchain Technologies}{January 2022 - May 2022}
    
\vspace{1pt}
    \resumeSubheading
    {Teaching Assistant}{Georgetown University}
    {Machine Learning Application Deployment, Advanced Math and Stat Computing}{August 2021 - December 2021}

\resumeSubHeadingListEnd

\end{document}